Water, High-Altitude Condensates, and Methane Depletion in the Atmosphere of the Warm Neptune WASP-107\lowercase{b}

### 2017-08-05 ms.tex
table

For the best fit white light curve, the root-mean-square (rms) residuals were 93 ppm (excluding the star spot crossing), which is somewhat larger than the expected shot noise of 50 ppm. We attribute the excess noise to loss of flux off the edge of the detector, which can occur if there is variation in the position or length of the spatial scan. There is no evidence for correlated noise in the residuals, so we increased the per-point uncertainties by a factor of 1.7 to achieve a reduced $\chi_2$ value of unity.  We used the Markov chain Monte Carlo algorithm to estimate parameter uncertainties \citep{foremanmackey13}.  The transit time was $t_0 = 2457910.45407\pm6\mathrm{e}{-5}$ and the planet/star radius was $r_p/r_s = 0.14399\pm0.00017$.

\subsection{Spectroscopic Light Curve Fits}
We binned the spectrum into 20 spectrophotometric channels from FIXME to FIXME $\mu$m, shown in Figure FIXME. We fit the light curves with the \texttt{divide-white} technique, which assumes that the light curve systematics are nearly constant as a function of wavelength \citep{stevenson??, kreidberg14a}. For this method, the transit model $T_\lambda(t)$ is multiplied by the systematics vector from the white light curve fit ($F_\mathrm{white}/T_\mathrm{white}$), and rescaled by a factor $C_\lambda + V_\lambda t$.  An advantage of this approach is that it removes the star spot crossing feature, enabling us to use orbit three with no additional correction. There is a small chromatic effect due to the changing amplitude of the spot crossing feature with wavelength, but this effect is below the level of noise in our data FIXME.  As for the white light curve, we fixed some of the transit parameters on the estimates from \cite{dai17} and fixed the limb darkening on the PHOENIX model. The fit has just three free parameters: $C_\lambda$, $V_\lambda$, and $r_p/r_s$.

The best fit light curves have a median reduced $\chi_2$ value of FIXME and rms values consistent with the expected photon shot noise.  There are two channels with slightly higher $\chi_2$ values: FIXME and FIXME. We therefore rescale the photometric uncertainties for all spectroscopic channels such that the $\chi_2$ values are unity, to ensure that we do not underestimate the uncertainty on the transit depths. We performed an MCMC fit to the light curves with \texttt{emcee}. The median transit depths and $1\,\sigma$ uncertainties are given in Table FIXME. FIXME: does the  median agree with the best fit? FIXME: convergence?

@@

\subsection{Independent Analysis}
We also performed an independent data reduction and fit using K. Stevenson's pipeline.

@@

>>>>

For the best fit white light curve, the root-mean-square (rms) residuals were 93 ppm (excluding the star spot crossing), which is somewhat larger than the expected shot noise of 50 ppm. We attribute the excess noise to loss of flux off the edge of the detector, which can occur if there is variation in the position or length of the spatial scan. There is no evidence for correlated noise in the residuals, so to account for the excess noise we simply increased the per-point uncertainties by a factor of 1.7 to achieve a reduced $\chi_2$ value of unity.  We then used the Markov chain Monte Carlo algorithm to estimate parameter uncertainties \citep{foremanmackey13}.  The transit time was $t_0 = 2457910.45407\pm6\mathrm{e}{-5}$ and the planet/star radius was $r_p/r_s = 0.14399\pm0.00017$.

\subsection{Spectroscopic Light Curve Fits}
We binned the spectrum into 20 spectrophotometric channels from 1.12 to 1.65 $\mu$m, shown in Figure\,\ref{fig:lc}. We fit the light curves with the \texttt{divide-white} technique, which assumes that the light curve systematics are nearly constant as a function of wavelength \citep{stevenson??, kreidberg14a}. For this method, the transit model $T_\lambda(t)$ is multiplied by the systematics vector from the white light curve fit ($F_\mathrm{white}/T_\mathrm{white}$), and rescaled by a factor $C_\lambda + V_\lambda t$.  An advantage of this approach is that it removes the star spot crossing feature, enabling us to use orbit three with no additional correction. There is a small chromatic effect due to the changing amplitude of the spot crossing feature with wavelength, but this effect is not detectable in our data.  As for the white light curve, we fixed some of the transit parameters on the estimates from \cite{dai17} and fixed the limb darkening on the PHOENIX model. The fit has just three free parameters: $C_\lambda$, $V_\lambda$, and $r_p/r_s$.

The best fit light curves have a median reduced $\chi_2$ value of 1.16.  To ensure that we do not underestimate the uncertainty on the transit depths, we rescale the photometric uncertainties for all spectroscopic channels such that the $\chi_2$ values are unity. We performed an MCMC fit to the light curves with \texttt{emcee}. The median transit depths and $1\,\sigma$ uncertainties are given in Table FIXME.

@@

\subsubsection{Independent Analysis}
We also performed an independent data reduction and fit using K. Stevenson's pipeline.

@@

\begin{deluxetable}{c c c}
\tablecaption{WASP-107b transmission spectrum \label{transit_depths}}
\tablehead{\colhead{Wavelength ($\mu$m)}  & \colhead{Transit depth} & \colhead{Uncertainty}}
\startdata
1.133 & 0.020641 & 5.9e-05 \\
1.158 & 0.020733 & 5.5e-05 \\
1.184 & 0.020505 & 5.6e-05 \\
1.209 & 0.020498 & 5.4e-05 \\
1.235 & 0.020455 & 5.9e-05 \\
1.260 & 0.020492 & 5.0e-05 \\
1.285 & 0.020620 & 6.2e-05 \\
1.311 & 0.020739 & 5.0e-05 \\
1.336 & 0.020660 & 5.7e-05 \\
1.362 & 0.020858 & 4.8e-05 \\
1.387 & 0.020794 & 4.8e-05 \\
1.413 & 0.020888 & 5.2e-05 \\
1.438 & 0.020821 & 6.2e-05 \\
1.464 & 0.020691 & 5.1e-05 \\
1.489 & 0.020682 & 6.9e-05 \\
1.515 & 0.020679 & 6.7e-05 \\
1.540 & 0.020509 & 6.0e-05 \\
1.565 & 0.020480 & 6.4e-05 \\
1.591 & 0.020500 & 5.6e-05 \\
1.616 & 0.020514 & 6.5e-05 \\
\enddata
\end{deluxetable}
